I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-10-20 paper_io_sim.tex
Add simulated platform descriptions

			Having our model validated, we create simulators for different use cases 
			using WRENCH.
			We integrate our I/O model to the original WRENCH by implementing 
			the core of the model separately from existing WRENCH components, 
			then providing an API for users to call to our simulation model. 
			We also add an optional command line argument so that users will be able 
			to choose use or not to use the model. Doing this, we can avoid 
			unexpected impacts on original WRENCH and can independently update 
			the model in the future. 
			We then compare the results of the simulators with
			original WRENCH and extended WRENCH with the results of real
			pipelines on a real system.

@@

        	The goal of our experiments is to evaluate our write-back cache 
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application 
            pipeline \textcolor{red}{[Maybe briefly describe this application's purpose (e.g. a standard fMRI preprocessing piepeline)]}, to evaluate the applicability of our simulation model.

@@

@@

			The simplest execution scenario is single-threaded, where memory 
			bandwidth and disk bandwidth are dedicated. Our goal is to 
			compare the detailed simulation results of each task in the pipeline 
			including read/write time, memory status and then validate the correctness 
			of the simulation model.

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20~GB, 50~GB, 75~GB and 100~GB, run 
			the pipeline on the cluster, measure the CPU time of the tasks  
			with each input and use it to simulate CPU time in the simulators .

			We simulate the pipeline with the Python prototype simulator, 
			a simulator with original WRENCH and another with WRENCH-Ext.

@@

			In the second experiment, we evaluate the simulator in a concurrent I/O, 
			bandwidth-sharing scenario with a multi-threaded application. 			
			We vary the number of concurrent pipelines running on a multi-core host.

@@

		We use the disk and memory benchmark results and CPU time measured from 
		the cluster to configure the simulated platform. The benchmark results of 
		bandwidths and configured values in the simulators are shown in \ref{table:benchmark}.

@@

		As read and write bandwidths are symmetrical in SimGrid, we take the average values 
		to configure our simulators.

>>>>

			Having the model validated, we create simulators for different use cases 
			using WRENCH.
			We integrate our I/O model to the original WRENCH by implementing 
			the core of the model separately from existing WRENCH components, 
			then providing an API for users to call to our simulation model. 
			We also add an optional command line argument so that users will be able 
			to choose use or not to use the model. Doing this, we can avoid 
			unexpected impacts on original WRENCH and can independently update 
			the model in the future. 
			We then compare the results of the simulators with
			original WRENCH and extended WRENCH with the results of real
			pipelines on a real system.

@@

        	The goal of our experiments is to evaluate our page cache 
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application 
            pipeline \textcolor{red}{[Maybe briefly describe this application's purpose (e.g. a standard fMRI preprocessing piepeline)]}, to evaluate the applicability of our simulation model.

@@

			In simulated platform description, because the disk bandwidths in SimGrid 
			are symmetrical, we measure the read/write bandwidths on our cluster and 
			take the average bandwidths. 
			As the pipelines are single-core, we create simulated tasks, 
			each of them runs on only one core. 
			While in Python, computation time can be directly configured, 
			this time is injected to the WRENCH simulators with number of flops, 
			which is calculated with CPU speed and compute duration. 
			In our experiments, the CPU speed is set to 1 Gflops. 
			Finally, because WRENCH simulates applications base on network-communication, 
			we use an infinite bandwidth to eliminate network latency for local I/Os.
			The details of simulated platform is available here: 
			https://github.com/dohoangdzung/wrench/blob/io_chunk_test/examples/basic-examples/io-pagecache/single_host.xml

@@

			The first experiment is single-threaded, where memory bandwidth 
			and disk bandwidth are dedicated. 
			Our goal is to compare the detailed simulation results of each task 
			in the pipeline including read/write time, memory behavior and 
			then validate the correctness of the simulation model.

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20~GB, 50~GB, 75~GB, 100~GB and run 
			the pipeline on the cluster.
			The pipeline is simulated with the Python prototype simulator, 
			original WRENCH and WRENCH with page cache simulator.

@@

			In the second scenario, we evaluate the simulator in a concurrent I/O, 
			bandwidth-sharing scenario with a multi-threaded application. 			
			We vary the number of concurrent pipelines running on a multi-core host.

@@

		The benchmark results of bandwidths and the values used in the simulators are shown in \ref{table:benchmark}. These configurations are used in all experiments.

@@
